---
title: "Simple document"
author: "Sijda Ahmed" 
date: 2025-09-11
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

I'm an R Markdown document! 

```{r echo=TRUE, message=FALSE}
library(tidyverse)
library(ggplot2)
```


# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3

This is where I'm going to to talk about code chunks.

```{r}
mean(samp)
sd(samp)
```

Let's also make a dataframe.

```{r}
example_df = 
  tibble(
    vec_numeric = 1:4,
    vec_char = c("My", "name", "is", "jeff"),
    vec_factor = factor(c("male", "male", "female", "female"))
  )
```

I'll create a new dataframe.

```{r}
new_df = 
  tibble(
    x = rnorm(100),
    y = 1 + 2 * x + rnorm(100)
  )
```

Let's make a plot and see how cool that is!

```{r}
plot_df = 
  tibble(
    x = rnorm(1000, mean = 1, sd = .5),
    y = 1 + 2 * x + rnorm(1000)
  )

ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

This is a neat scatterplot!

# Learning Assesement

This chunk does one of the LA.

```{r}
la_df =
  tibble(
    numeric_samp = rnorm(500, mean=1),
    greather_0 = numeric_samp > 0,
    abs_val_samp = abs(numeric_samp)
  )

ggplot(la_df, aes(x = abs_val_samp)) + geom_histogram()

median_samp = median(pull(la_df, numeric_samp))
```

The median of the variable containing absolute values is `r round(median_samp, digits = 2)`.

"The sample size in the new dataframe is `r nrow(la_df)`."

Something more complex is "The mean of my new variable is`r mean(pull(la_df, abs_val_samp))`."

If I want to talk about `la_df`, I would use the backticks.

